Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2016-02-08 documents/ms/ms.tex
Hogg's first 12 pages of comments

\usepackage{natbib}

%\graphicspath{{figures/png/}}

\newcommand{\notenglish}[1]{\textit{#1}}
\newcommand{\sic}{\notenglish{sic}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Kepler}{\project{Kepler}}
\newcommand{\name}{CPM}
\newcommand{\set}[1]{\mathcal{#1}}
\newcommand{\given}{\,|\,}
\newcommand{\todo}[1]{\textbf{#1}}
\newcommand{\revise}[1]{\textcolor{green}{#1}}
\newcommand{\remove}[1]{\sout{#1}}

@@

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
the most precise photometric measurements of stars ever made---%
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level so that
it can capture very fine-grained information about the variation of the spacecraft.
\remove{The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star.} \revise{The CPM models the systematic effects in the time series of a pixel using the pixels
around many other stars and the assumption that any shared signal in
these causally disconnected light curves is caused by instrumental
effects.} In addition, we use the target star's future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four \remove{hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components),}
\revise{tuning parameters---the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components,}
 which we set by cross-validation. 
We determine a generic set of \remove{hyper-parameters}\revise{tuning parameters} that works well for most of the stars and apply the method to a corresponding set of target stars.
\remove{We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.} 
\revise{We find that \name\ can consistently produce relatively low-noise (CDPP) light-curves. In this paper, we demonstrate that pixel-level de-trending is possible while retaining transit signals (with a train-and-test framework) and we think that methods like \name\ is generally applicable and might be useful for  K2, TESS, etc, where the data aren't these clean postage stamps like \Kepler.}

@@

The photometric measurements of stars made by the \Kepler\ \remove{satellite}\revise{space craft} are precise enough
  to permit discovery of exoplanet transits with depths smaller than $10^{-4}$.
This precision results from great spacecraft stability,
  supplemented by various methods for removing small residual spacecraft-induced and stellar-variability trends in the brightnesses,
  either filtering the data (with things like median filters)
  or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; 
  \cite{gaussian}).
When employed in the service of exoplanet search and characterization,
  these methods are usually agnostic about whether photometric variations originate in the spacecraft or in the star itself;
  that is, they obliterate intrinsic stellar variability along with spacecraft issues.

In general, there are many reasons for apparent photometric variability in a \Kepler\ source.
There is intrinsic stellar variability,
  which is of interest to some and a nuisance to others.
There is also variability of overlapping fainter stars;
  that is, confusion noise combined with variability of the confusing sources.
There are small changes in spacecraft pointing,
  which leads to slightly different illumination of the focal-plane pixels,
  and thus different sensitivity to variations in the device.
There are also \emph{intra-pixel} sensitivity variations that can contribute, which was first measured by \revise{\cite{subpixel}}.
There are small changes in spacecraft temperature,
  which lead to point-spread function (PSF) and differential \remove{(across the focal plane)} pointing changes.
These also lead to changes in pixel and intra-pixel illumination.
Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
There is electronic cross-talk between detectors and charge-transfer inefficiency;
  these can effectively transfer variability from one source to another.
There are additional electronics effects like ``rolling bands'' that put additional features into light-curves \revise{\citep{handbook}}.
There are also \remove{probably} changes to the detector sensitivity with temperature and time,
  possibly illimunation-history effects,
  and possibly sources of variability not yet considered.
The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
  much higher than ever previously attempted;
  new effects really \emph{must} appear at some point.
In \figurename~\ref{ccd}, we show the pixel-level variability in the \Kepler\ data
  near one bright star that shows minimal intrinsic variability;
  this figure highlights the spacecraft-induced effects.

@@

One such method---one that is designed to describe or model spacecraft-induced problems
  but \emph{not} interfere with measurements of stellar variability---%
  is the \Kepler\ Presearch \remove{(\sic)} Data Conditioning (PDC, \cite{pdc1}).
The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities. 
%This seems the original paper on PDC:
%[PDC1] https://kepler.nasa.gov/science/ForScientists/papersAndDocumentation/SOCpapers/7740-67-pdc-jtwicken-copyright.pdf
%
%This describes the later version of PDC:
%[PDC2] http://arxiv.org/pdf/1203.1382v1.pdf
%[PDC3] http://arxiv.org/pdf/1203.1383v1.pdf

@@

In \cite{pdc2,pdc3}\remove{, filtered light-curves of other stars are used instead. 
The light-curve of a target star is projected on the leading eight principal components of these light-curves. 
This projection is then removed from the star's light-curve. 
The principal components are computed from a set of relatively quiet stars close in position and magnitude. 
This was done since it was observed that otherwise, too much of the stellar variability was being removed.}

\revise{In the most recent version of PDC (PDC-MAP, \cite{pdc2,pdc3}), filtered light-curves of other stars are used
instead. Using a set of relatively quiet stars on each detector, the
top 8 principle components are computed for every quarter of Kepler
data. The maximum a posteriori linear combination of these basis light
curves---computed using an empirical prior on the trend
magnitudes---are used to model and remove the systematics in all the
Kepler light curves. The choice to use such a small number of
components and to apply priors was made in order to reduce
over-fitting and retain physical signals after systematics removal.}

@@

PDC \remove{``de-trends''}\revise{"co-trends" or calibrates} the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
  generated from a principal components analysis (PCA) of filtered light-curves.
That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
  by filtering and restricting the dimensionality (through PCA).

The method proposed here, \name, shares the motivation of PDC.
The main differences are that
\begin{enumerate}
\item
\name\ works in the pixel domain, not the light-curve domain, so it has access to more fine-grained information
\item
\name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the light-curves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework. 
  \revise{PDC mitigates overfitting by
reducing the freedom of the model and applying empirical priors to the
fit coefficients.}
\item 
\name\ directly optimizes for prediction accuracy, while PDC uses PCA projections.
\item
\remove{the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
  variability is also removed as well as the systematics.}
  \revise{The current version of \name\ is
tuned to remove systematics while minimizing the impact on exoplanet
transit signals. It makes no attempt to retain lower frequency signals
that can be produced by other astrophysical signals.}
\item 
\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light-curves) of the other stars.
\end{enumerate}

The two methods (\name\ and PDC) are similar however,
  in that they both make the \remove{(implicit or explicit)} assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
  must also be imprinting similar or related variability on other light-curves.
\remove{In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).}
By going to the pixel level (unlike the PDC, which works at the photometry level),
  \name\ makes it easier for the model to capture variability
  that is coming through variations in the centroids and point-spread function
  from spacecraft pointing, roll, and temperature.

Before we start, a few reminders about the \Kepler\ data are in order:
The \remove{satellite}\revise{space craft} \remove{always observes}\revise{observed} precisely the same field, at fixed pointing (as closely as possible).
\revise{About 6\% of the 96,465,600 pixels}\remove{Only a few percent of the 80 million pixels} in the focal plane are telemetered down
  to Earth from each 30-min exposure;
  the telemetered pixels are associated with \Kepler\ target stars chosen for study by the \Kepler\ Team \revise{(along with a non-trivial set collateral pixels used for calibration)}.
The \remove{satellite}\revise{space craft} is rolled by 90~deg every \remove{90-ish}\revise{93} days (to satisfy Solar-Angle constraints).
The focal plane contains many CCDs;
  this plus the 90-deg rotations means that each star is at a particular location
  on a particular CCD for \remove{90-ish-day}\revise{quarter} contiguous periods of time.
The PSF varies strongly across the field and is badly sampled.
The stars span a huge range in brightness;
  some of \Kepler's most important targets even saturate the device and bleed charge.
The stellar photometry returned by the \Kepler\ SAP and PDC pipelines is based on
  straight, \emph{unweighted} sums of pixels in small patches centered on the stellar centroid.
We will return to this latter point at the end;
  this kind of photometry cannot be optimal;
  it must be possible to do a better job with the photometric measurements.
That's beyond the scope of this project but a place for a valuable intervention on the \Kepler\ data.

@@

The point of these models is to be \emph{flexible},
  so the usual approach is to make the input data set very large,
  and the number of parameters large,
  often as large as---or larger than---the target data available.
Such fits require \emph{regularization} to break degeneracies
  and control ill-constrained parameters.
These regularizations do for optimizations what priors do for posterior probability inferences;
  they express the desired behavior of the fit in the absence of data
  or along directions in parameter space in which the data are not constraining.
General regularizations or priors will break the convexity of linear model fitting;
  if convexity is to be maintained, these regularizations also have to be quadratic,
  or else one of a class of other known forms (one of which is L1-regularization).
Given these considerations, it makes sense to try to build our pixel-level model
  using a linear model with a quadratic objective function and a quadratic regularization;
  this is what \name\ will be.

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.4\textwidth]{f1a}
\includegraphics[width=0.4\textwidth]{f1b}
\end{center}
\caption{
  \label{ccd} 
  Stars on the same CCD share systematic errors. 
  The two panels show pixel fluxes (brightnesses) for two stars in quarter 5. \emph{Left:} KIC 5088536, \emph{Right:} KIC 5949551; 
  here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
  but far enough apart such that there is no stray light from one affecting the other. 
  Each panel shows the pixels contributing to the respective star.
  Note that there exist similar trends in these two stars, caused by systematic errors. 
%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
}
\end{figure}

@@

In this framework, the data used to \emph{train} the model%
  ---meaning set the values of the parameters of the model---%
  are disjoint from the \emph{test} data
  ---meaning the data that are being predicted (the target data).
Because we are concerned with detecting exoplanet transits,
  which take few hours,
  we adopt an extreme version of the train-and-test framework,
  in which the training data are always separated from the test data by couple of hours.
That is, when we are using the model to predict a particular pixel in the target data taken at time $t$,
  we use parameters obtained by an optimization that makes use of only data
  that comes either at times prior to $t-\Delta t$ or after $t+\Delta t$,
  where $\Delta t$ is a tunable parameter but which we will set to $9$~h.
This ensures that no information about any exoplanet transit itself
  can be entering into the prediction of the pixels contributing to the stellar photometry.
In general, if there is a scientific goal of preserving intrinsic stellar variability,
  or transit signals,
  on time-scales of $\tau$,
  the parameter optimization ought to be based on training data taken with a time-exclusion zone of half-width $\Delta t > \tau$.

In addition, 
  each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 30$\,d.
The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
  effectively assumes that the signals worth preserving have time-scales less than $\Delta t$ 
  but don't recur on time-scales shorter than $t_{\max}$.
Those assumptions are good for our purposes but not necessarily ideal for all users:
Short-period exoplanets and certain kinds of stellar variability
  could be wiped out by a model with these settings of the training-data regime.

The fourth general idea involved in this kind of data-driven modelling is that the models often aren't \emph{interpretable}, 
  or at least are hard to interpret.
This means, in particular, that although the model might do a good job of \emph{predicting} the target pixels,
  using a linear (or more complex) combination of the input pixel data,
  it won't deliver anything that can be unambiguously interpreted as the \emph{flux} of the star in question,
  or any other signal we care about.
The data-driven model \emph{effectively} describes the pointing, point-spread function, and flat-field
  of the telescope and camera,
  plus the variability of every star and every exoplanet transit,
  but it does so without ever \emph{explicitly} creating any of those objects.
We have to make some kind of heuristic or interpretive move to extract from the data-driven model the quanitites of interest.

Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
  that any particular data-driven model is better or worse than any other.
This problem is a problem for \name, and for the \Kepler\ PDC, and any other data-driven calibration models.
One might think that the ``best'' model is the one that predicts data with lowest variance;
  this would be true if all models adhered to the same train-and-test framework, which they don't.
Besides, a model that can predict not just the spacecraft-induced variability,
  but also variability caused by exoplanet transits of interest,
  will effectively over-fit and distort the most important information in the light-curves.
That is, what is considered best for modelling the data depends on the objectives of the user.
For us, who are interested (in the long term) in finding and characterizing Earth analogs,
  the ``best'' data-driven model is the one that produces the most success in finding and characterizing Earth analogs!
What we will show in what follows is that the \name\ photometry does not distort
  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data
  and promising properties of the \name\ outputs \revise{on real Kepler light-curves}.
In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.

We also want to emphasis that all the calibration in this paper for \Kepler is 
  based on the assumption that the device is \remove{'self-calibratable'}\revise{can be self-calibrated}, 
  which means all the information we need to calibrate the device are contained in the device itself 
  (either in science data or engineering data) and no external information, 
  for example, measurements from other device, are needed.
  And a description of the method in the machine learning context can be found in \cite{icml2015}

\section{\name\ specification and \revise{tuning parameters}}
\subsection{\name\ model}
Each individual \Kepler\ target star is, for each quarter (each \remove{90-ish-day})
  on a particular CCD on the \Kepler\ focal plane.
Associated with each target star is some set of pixels,
  located in a small contiguous patch \remove{more-or-less} centered on the target star,
  and telemetered down once for every 30-min exposure.
Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.
That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.

Let's consider a particular pixel $m$ in the focal plane in one particular month
  (here we always use data per month rather than quarter,  since there are discontinuities between every \remove{30-ish-day period}\revise{month}).
In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{m,n}$
  of the intensity falling in pixel $m$ at the $N$ times $t_n$ at which exposures were taken during the month.
(For intensity measurements $I_{m,n}$ here we are using pixels from \revise{the FLUX column of Target Pixel File, which is flux of each pixel after processed by the pipeline module CAL, the removal of the interpolated background, and the removal of cosmic rays} on MAST
  \footnote{\url{http://archive.stsci.edu/kepler/}}, for details of the TPF, 
  see the \project{Kepler Archive Manual} 
  \footnote{\url{http://archive.stsci.edu/kepler/manuals/archive_manual.pdf}}).
We want to build a prediction for the intensity $I_{m,n}$ in pixel $m$ at each time $t_n$
  using the intensities $I_{m',n}$ of other pixels $m'$.
The question is:  What other pixels to choose?
There are many possible qualitatively and quantitatively different choices here.
Assuming that they are affected by similar systematic errors as the target star pixels, 
  we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter that are closest in magnitude
  (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
  to the target star associated with pixel $m$.
This set of pixels%
  ---from the $Q$ stars on the same CCD---%
  is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
  \remove{To rule out any direct optical cross-talk by starry light}
  \revise{To minimize the effects of blending with and crosstalk from nearby stars}, we require that the predictor pixels are \remove{from stars
sufficiently far away from the target star (at least 20 pixels distance on the CCD).}
\revise{from stars at least 20 pixels away from the target star.}
Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
  than the star associated with pixel $m$, and are far from it on CCD, 
  the pixel $m$ will not be in the set $\set{M}_m$,
  and nor will any of pixel $m$'s close neighbors.
That is, there will be no (or almost no) overlap in stellar illumination of pixel $m$
  and the pixels $m'\in\set{M}_m$.

>>>>

\usepackage{natbib}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
%\graphicspath{{figures/png/}}
\definecolor{darkgreen}{RGB}{0, 64, 0}

\newcommand{\notenglish}[1]{\textit{#1}}
\newcommand{\sic}{\notenglish{sic}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Kepler}{\project{Kepler}}
\newcommand{\name}{CPM}
\newcommand{\set}[1]{\mathcal{#1}}
\newcommand{\given}{\,|\,}
\newcommand{\todo}[1]{\textbf{#1}}
\newcommand{\revise}[1]{\textcolor{darkgreen}{#1}}
\newcommand{\remove}[1]{\sout{#1}}

@@

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
the most precise photometric measurements of stars ever made---%
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level so that
it can capture very fine-grained information about the variation of the spacecraft.
\remove{The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star.} \revise{The CPM models the systematic effects in the time series of a pixel using the pixels
of many other stars and the assumption that any shared signal in
these causally disconnected light curves is caused by instrumental
effects.} In addition, we use the target star's future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four \remove{hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components),}
\revise{tuning parameters---the number of predictor stars or pixels, the auto-regressive window size, 
and two L2-regularization amplitudes for model components,}
 which we set by cross-validation. 
We determine  \remove{a generic set ofhyper-parameters}\revise{values for tuning parameters} that works well for most of the stars and apply the method to a corresponding set of target stars.
\remove{We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.} 
\revise{We find that \name\ can consistently produce low-noise light-curves. In this paper, we demonstrate that pixel-level de-trending is possible while retaining transit signals and we think that methods like \name\ are generally applicable and might be useful for  K2, TESS, etc, where the data aren't clean postage stamps like \Kepler.}

@@

The photometric measurements of stars made by the \Kepler\ \remove{satellite}\revise{spacecraft} are precise enough
  to permit discovery of exoplanet transits with depths smaller than $10^{-4}$.
This precision results from great spacecraft stability,
  supplemented by various methods for removing small residual spacecraft-induced and stellar-variability trends in the brightnesses,
  either filtering the data (with things like median filters)
  or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; 
  \citealt{gaussian}).
When employed in the service of exoplanet search and characterization,
  these methods are usually agnostic about whether photometric variations originate in the spacecraft or in the star itself;
  that is, they obliterate intrinsic stellar variability along with spacecraft issues.

In general, there are many reasons for apparent photometric variability in a \Kepler\ source.
There is intrinsic stellar variability,
  which is of interest to some and a nuisance to others.
There is also variability of overlapping fainter stars;
  that is, confusion noise combined with variability of the confusing sources.
There are small changes in spacecraft pointing,
  which leads to slightly different illumination of the focal-plane pixels,
  and thus different sensitivity to variations in the device.
There are also \emph{intra-pixel} sensitivity variations that can contribute\revise{(\citealt{subpixel})}.
There are small changes in spacecraft temperature,
  which lead to point-spread function (PSF) and differential \remove{(across the focal plane)} pointing changes.
These also lead to changes in pixel and intra-pixel illumination.
Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
There is electronic cross-talk between detectors and charge-transfer inefficiency;
  these can effectively transfer variability from one source to another.
There are additional electronics effects like ``rolling bands'' that put additional features into light-curves \revise{\citep{handbook}}.
There are also \remove{probably} changes to the detector sensitivity with temperature and time,
  possibly illimunation-history effects,
  and possibly other sources of variability not yet considered.
The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
  much higher than ever previously attempted;
  new effects really \emph{must} appear at some point.
In \figurename~\ref{ccd}, we show the pixel-level variability in the \Kepler\ data
  near one bright star that shows minimal intrinsic variability;
  this figure highlights the spacecraft-induced effects.

@@

One such method---one that is designed to describe or model spacecraft-induced problems
  but \emph{not} interfere with measurements of stellar variability---%
  is the \Kepler\ Presearch \remove{(\sic)} Data Conditioning (PDC, \citealt{pdc1}).
The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities.

@@

\remove{In \cite{pdc2,pdc3}, filtered light-curves of other stars are used instead. 
The light-curve of a target star is projected on the leading eight principal components of these light-curves. 
This projection is then removed from the star's light-curve. 
The principal components are computed from a set of relatively quiet stars close in position and magnitude. 
This was done since it was observed that otherwise, too much of the stellar variability was being removed.}

\revise{In the most recent version of PDC (PDC-MAP, \citealt{pdc2,pdc3}), filtered light-curves of other stars are used. Using a set of relatively quiet stars on each detector, the
top 8 principal components are computed for every quarter of Kepler
data. The maximum a posteriori linear combination of these basis light
curves---computed using an empirical prior on the trend
magnitudes---are used to model and remove the systematics in all the
Kepler light curves. The choice to use such a small number of
components and to apply priors was made in order to reduce
over-fitting and retain physical signals after systematics removal.}

@@

PDC \remove{``de-trends''}\revise{``co-trends'' or calibrates} the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
  generated from a principal components analysis (PCA) of filtered light-curves.
That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
  by filtering and restricting the dimensionality (through PCA).

The method proposed here, The Causal Pixel Model(\name), shares the motivation of PDC.
The main differences are that
\begin{enumerate}
\item
\name\ works in the pixel domain, not the light-curve domain, so it has access to more fine-grained information
\item
\name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the light-curves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework. 
  \revise{PDC mitigates overfitting by
reducing the freedom of the model and applying empirical priors to the
fit coefficients.}
\item 
\name\ directly optimizes for prediction accuracy, while PDC uses PCA projections.
\item
\remove{the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
  variability is also removed as well as the systematics.}
  \revise{The current version of \name\ is
tuned to remove systematics while minimizing the impact on exoplanet
transit signals. It makes no attempt to retain lower frequency signals
that can be produced by other astrophysical signals.}
\item 
\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light-curves) of the other stars.
\end{enumerate}

The two methods (\name\ and PDC) are similar however,
  in that they both make the \remove{(implicit or explicit)} assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
  must also be imprinting similar or related variability on other light-curves.
\remove{In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).}
By going to the pixel level (unlike the PDC, which works at the stellar-photometry level),
  \name\ makes it easier for the model to capture variability
  that is coming through variations in the centroids and point-spread function
  from spacecraft pointing, roll, and temperature.

Before we start, a few reminders about the \Kepler\ data are in order:
The \remove{satellite}\revise{spacecraft} \remove{always observes}\revise{observed} precisely the same field, at fixed pointing (as closely as possible).
\revise{About 6 percent of the 96,465,600 pixels}\remove{Only a few percent of the 80 million pixels} in the focal plane are telemetered down
  to Earth from each 30-min exposure;
  the telemetered pixels are associated with \Kepler\ target stars chosen for study by the \Kepler\ Team \revise{(along with a non-trivial set of collateral pixels used for calibration)}.
The \remove{satellite}\revise{spacecraft} is rolled by 90~deg every \remove{90-ish}\revise{93} days (to satisfy Solar-Angle constraints).
The focal plane contains many CCDs;
  this plus the 90-deg rotations means that each star is at a particular location
  on a particular CCD for \remove{90-ish-day}\revise{quarter} contiguous periods of time.
The PSF varies strongly across the field and is poorly sampled.
The stars span a huge range in brightness;
  some of \Kepler's most important targets even saturate the device and bleed charge.
The stellar photometry returned by the \Kepler\ SAP and PDC pipelines is based on
  straight, \emph{unweighted} sums of pixels in small patches centered on the stellar centroid.
We will return to this latter point at the end;
  this kind of photometry cannot be optimal;
  it must be possible to do a better job with the photometric measurements.
That's beyond the scope of this project but a place for a valuable intervention on the \Kepler\ data.

@@

The point of these models is to be \emph{flexible},
  so the usual approach is to make the input data set very large,
  and the number of parameters large,
  often as large as---or larger than---the target data available.
Such fits require \emph{regularization} to break degeneracies
  and control ill-constrained parameters.
These regularizations do for optimizations what priors do for posterior probability inferences;
  they express the desired behavior of the fit in the absence of data
  or along directions in parameter space in which the data are not constraining.
\remove{General} Regularizations or priors \remove{will}\revise{can} break the convexity of linear model fitting;
  if convexity is to be maintained, these regularizations also have to be quadratic,
  or else one of a class of other known forms (one of which is L1-regularization).
Given these considerations, it makes sense to try to build our pixel-level model
  using a linear model with a quadratic objective function and a quadratic regularization;
  this is what \name\ will be.

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.4\textwidth]{f1a}
\includegraphics[width=0.4\textwidth]{f1b}
\end{center}
\caption{
  \label{ccd} 
  Stars on the same CCD share systematic errors. 
  The two panels show pixel fluxes (brightnesses) for two stars in quarter 5. \emph{Left:} KIC 11351420, \emph{Right:} KIC 11401755; 
  here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
  but far enough apart such that there is no stray light from one affecting the other. 
  Each panel shows the pixels contributing to the respective star.
  Note that there exist similar trends in these two stars, caused by systematic errors. 
%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
}
\end{figure}

@@

In this framework, the data used to \emph{train} the model%
  ---meaning set the values of the parameters of the model---%
  are disjoint from the \emph{test} data
  ---meaning the data that are being predicted (the target data).
Because we are concerned with detecting exoplanet transits,
  which take a few hours,
  we adopt an extreme version of the train-and-test framework,
  in which the training data are always separated from the test data by \remove{several}\revise{many} hours.
That is, when we are using the model to predict a particular pixel in the target data taken at time $t$,
  we use parameters obtained by an optimization that makes use of only data
  that comes either at times prior to $t-\Delta t$ or after $t+\Delta t$,
  where $\Delta t$ is a tunable parameter \remove{but} which we will set to $9$~h.
This ensures that no information about any \revise{sufficiently short} exoplanet transit itself
  can be entering into the prediction of the pixels contributing to the stellar photometry.
In general, if there is a scientific goal of preserving intrinsic stellar variability,
  or transit signals,
  on time-scales of $\tau$,
  the parameter optimization ought to be based on training data taken with a time-exclusion zone of half-width $\Delta t > \tau$.

In addition, 
  each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 30$\,d.
The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
  effectively assumes that the signals worth preserving have time-scales less than $\Delta t$ 
  but don't recur on time-scales shorter than $t_{\max}$.
Those assumptions are good for our purposes but not necessarily ideal for all users:
Short-period exoplanets and certain kinds of stellar variability
  could be wiped out by a model with these settings of the training-data \remove{regime}\revise{bounaries}.

The fourth general idea involved in this kind of data-driven modelling is that the models often aren't \emph{interpretable}, 
  or at least are hard to interpret.
This means, in particular, that although the model might do a good job of \emph{predicting} the target pixels,
  using a linear (or more complex) combination of the input pixel data,
  it won't deliver anything that can be unambiguously interpreted as the \emph{flux} of the star in question,
  or any other signal we care about.
The data-driven model \emph{effectively} describes the pointing, point-spread function, and flat-field
  of the telescope and camera,
  plus the variability of every star and every exoplanet transit,
  but it does so without ever \emph{explicitly} creating any of those objects.
We have to make some kind of heuristic or interpretive move to extract from the data-driven model the quantities of interest.

Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
  that any particular data-driven model is better or worse than any other.
This problem is a problem for \name, and for the \Kepler\ PDC, and any other data-driven calibration models.
One might think that the ``best'' model is the one that predicts data with lowest variance;
  this would be true if all models adhered to the same train-and-test framework, which they don't.
Besides, a model that can predict not just the spacecraft-induced variability,
  but also variability caused by exoplanet transits of interest,
  will effectively over-fit and distort the most important information in the light-curves.
That is, what is considered best for modelling the data depends on the objectives of the user.
For us, who are interested (in the long term) in finding and characterizing Earth analogs,
  the ``best'' data-driven model is the one that produces the most success in finding and characterizing Earth analogs!
What we will show in what follows is that the \name\ photometry does not distort
  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data
  \remove{and promising properties of the \name\ outputs}.
In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.

We also want to emphasis that all the calibration in this paper for \Kepler\ is 
  based on the assumption that the device \remove{is 'self-calibratable'}\revise{can be self-calibrated}, 
  which means all the information we need to calibrate the device are contained in the \remove{device itself 
  (either in} science data \remove{or engineering data)} and no external information, 
  for example, measurements from \revise{any} other device, are needed.
\remove{Description}\revise{Elaboration} of the method in \remove{the}\revise{a} machine learning context can be found in \cite{icml2015}

\section{\name\ specification and \revise{tuning parameters}}
\subsection{\name\ model}
Each individual \Kepler\ target star is, for each quarter \remove{(each 90-ish-day)},
  \revise{in a particular location} on a particular CCD on the \Kepler\ focal plane.
Associated with each target star is some set of pixels,
  located in a small contiguous patch \remove{more-or-less} centered on the target star,
  and telemetered down once for every 30-min exposure.
Here we are ignoring all short-cadence data that \remove{is}\revise{are} taken in a different mode with shorter exposures.
That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.

\remove{Let's} Consider a particular pixel $m$ in the focal plane in one particular month
  (here we always use data per month rather than quarter,  since there are discontinuities between every \remove{30-ish-day period}\revise{months}).
In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{m,n}$
  of the intensity falling in pixel $m$ at the $N$ times $t_n$ at which exposures were taken during the month.
(For intensity measurements $I_{m,n}$ \remove{here} we are using pixels from \revise{the FLUX column of Target Pixel File, which is flux of each pixel after processed by the pipeline module CAL, the removal of the interpolated background, and the removal of cosmic rays} on MAST
  \footnote{\url{http://archive.stsci.edu/kepler/}}, for details of the TPF, 
  see the \project{Kepler Archive Manual} 
  \footnote{\url{http://archive.stsci.edu/kepler/manuals/archive_manual.pdf}}).
We want to build a prediction for the intensity $I_{m,n}$ in pixel $m$ at each time $t_n$
  using the intensities $I_{m',n}$ of other pixels $m'$.
The question is:  What other pixels to choose?
There are many possible qualitatively and quantitatively different choices here.
Assuming that they are affected by similar systematic errors as the target star pixels, 
  we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter that are closest in magnitude
  (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
  to the target star associated with pixel $m$.
This set of pixels%
  ---from the $Q$ stars on the same CCD---%
  is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
  \remove{To rule out any direct optical cross-talk by starry light}
  \revise{To minimize the effects of blending with, and crosstalk from, nearby stars}, we require that the predictor pixels are \remove{from stars
sufficiently far away from the target star (at least 20 pixels distance on the CCD).}
\revise{from stars at least 20 pixels away from the target star.}
Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
  than the star associated with pixel $m$, and are far from it on CCD, 
  the pixel $m$ will not be in the set $\set{M}_m$,
  and nor will any of pixel $m$'s close neighbors.
That is, there will be no (or almost no) overlap in stellar illumination of pixel $m$
  and the pixels $m'\in\set{M}_m$.
